---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sagemaker

<!-- badges: start -->
<!-- badges: end -->

The sagemaker R package provides a simplified interface
to the AWS Sagemaker API by:

1. adding sensible defaults so you can dive in quickly

2. creating helper functions to streamline model analysis

3. supporting `data.frame`s and [tibbles](https://github.com/tidyverse/tibble)

Check out the 
[Get started](https://tmastny.github.io/sagemaker/articles/sagemaker.html) 
guide for examples!

## Installation

You can install sagemaker from [GitHub](https://github.com/) with:
```r
# install.packages("devtools")
devtools::install_github("tmastny/sagemaker")
```

You will also need `boto3`, `sagemaker`, and `awscli` 
python packages.
If you don't have them, or aren't sure, install with:
```r
sagemaker::sagemaker_install()
```

Next, you'll need an [AWS account](https://aws.amazon.com/premiumsupport/knowledge-center/create-and-activate-aws-account/). 
This is a complicated process and unfortunately I don't have a good guide
to share. Please reach out if you find one and I'll post it here!

Once you have the account and user setup you'll want to
save your account access keys. 
[This](https://www.viget.com/articles/set-up-aws-cli-and-download-your-s3-files-from-the-command-line/)
is a good guide to follow.

Lastly, you need a AWS Sagemaker Execution Role.
The easiest way is to create a AWS Sagemaker Notebook Instance. 
Try [this guide](https://sagemaker-workshop.com/introduction/notebook.html#launch-the-notebook-instance)
to get the notebook running.
Once the notebook is deployed, *inside the instance* run:
```python
from sagemaker import get_execution_role

role = get_execution_role()
print(role)
```

Once you have that role, 
run this command locally 
to save it with your local AWS config:
```r
sagemaker::sagemaker_save_execution_role(
  "arn:aws:iam::[account_number]:role/service-role/[SageMakerExecutionRole]"
)
```

## Streamlined Analysis

Compare the AWS Sagemaker API vs. to the sagemaker R package yourself 
with this [side-by-side comparsion](https://tmastny.github.io/sagemaker/articles/sagemaker-vs-sagemaker.html) 
. 
The R package hides the details for latter, 
and lets you get started ASAP.

You start with this:

```{r eval = FALSE}
library(sagemaker)
xgb <- sagemaker_xgb_estimator()
```

instead of this:

```{r eval = FALSE}
library(reticulate)
sagemaker <- reticulate::import("sagemaker")
boto3 <- reticulate::import("boto3")

xgb_container <- sagemaker$amazon$amazon_estimator$get_image_uri(
  boto3$Session()$region_name,
  "xgboost",
  repo_version = "latest"
)

xgb <- sagemaker$estimator$Estimator(
  xgb_container,
  sagemaker_get_execution_role(),
  train_instance_count = 1L,
  train_instance_type = "ml.m4.xlarge",
  output_path = s3(s3_bucket(), "/models/"),
  sagemaker_session = sagemaker$Session()
)
```

## 
