---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sagemaker

<!-- badges: start -->
<!-- badges: end -->

The sagemaker R package provides a simplified API to AWS Sagemaker. 
The goal is to provide an R interface
that uses sensible defaults 
so you can quickly train and analyze machine learning models.

## Installation

You can install sagemaker from [GitHub](https://github.com/) with:
```r
# install.packages("devtools")
devtools::install_github("tmastny/sagemaker")
```

## Simplify

See the Sagemaker vs. Sagemaker
[side-by-side comparsion](https://tmastny.github.io/sagemaker/articles/sagemaker-vs-sagemaker.html) 
yourself. 
The R package hides the details for latter, 
and lets you get started ASAP.

You can start with this:

```{r eval = FALSE}
library(sagemaker)
xgb <- sagemaker_xgb_estimator()
```

instead of this:

```{r eval = FALSE}
library(reticulate)
sage <- reticulate::import("sagemaker")
boto3 <- reticulate::import("boto3")

xgb_container <- sagemaker$amazon$amazon_estimator$get_image_uri(
  boto3$Session()$region_name,
  "xgboost",
  repo_version = "latest"
)

xgb <- sagemaker$estimator$Estimator(
  xgb_container,
  sagemaker_get_execution_role(),
  train_instance_count = 1L,
  train_instance_type = "ml.m4.xlarge",
  output_path = s3(s3_bucket(), "/models/"),
  sagemaker_session = sagemaker$Session()
)
```


